Hemispheric Lateralization in ICH

### 2023-09-09 code/dataAnalysis/logistic.qmd
ordinal

---
title: "Hemispheric Lateralization in ICH"
subtitle: "Logistic Regression"
author: "Nikhil Patel"
project:
  type: default
format:
  html:
    code-fold: true
    code-tools: true
    toc: true
    html-math-method: katex
    css: "styles.css"
---

```{r hemisphere only}
priors <- c(prior())

>>>>

---
title: "Hemispheric Lateralization in ICH"
subtitle: "Logistic Regression"
author: "Nikhil Patel"
project:
  type: default
format:
  html:
    code-fold: false
    code-tools: true
    toc: true
    html-math-method: katex
    css: "styles.css"
---

We are trying to see if there is an association between hemispheric laterality and outcomes. The outcomes we have are both functional disability as measured by the mRS and quality of life as measured by the EuroQOL.

```{r setup, warning=FALSE, message=FALSE}

# import libraries
library(bayesrules)
library(tidyverse)
library(brms)
library(cmdstanr)
library(rstanarm)
library(marginaleffects)
library(broom)
library(broom.mixed)
library(tidybayes)
library(ggdist)
library(patchwork)
library(scales)
library(qs)

# call this once to distribute chains across cpu cores:
options(mc.cores = parallel::detectCores())

# plot themes
colors <- MetBrewer::met.brewer("Derain", 6)
theme_set(theme_bw())

# Tell bayesplot to use the viridis rocket palette for things like pp_check()
viridisLite::viridis(6, option = "rocket", end = 0.85, direction = -1) |>
  # Take off the trailing "FF" in the hex codes
  map_chr(~ str_sub(., 1, 7)) |>
  bayesplot::color_scheme_set()

# import data
d <- qread("../../data/nindsCombined.qs")
